### 2022-05-24 main/chapter_2ljets.tex
fill in alt triggers

The loosest triggers are `prescaled' --- their data rate is reduced by randomly
accepting only a small fraction of events.
For $\twoljets$, we use only the `lowest' (loosest, highest rate) un-prescaled
triggers selecting two charged leptons~\cite{atlas_twiki_lowest_unprescaled}.
Those charged leptons are selected in the
high-level trigger (described in Section~\ref{sec:atlas_trigger})
primarily requiring large $\pt$ and certain quality criteria which vary by
trigger.

@@

\subsubsection{Alternative triggers}
\textit{Knut Vadla} \TODO

@@

\subsection{Fake/non-prompt leptons}

>>>>

The loosest triggers are `prescaled' --- their data rate is reduced by randomly
accepting only a small fraction of events.
Prescaling adds complication which we avoid;
for $\twoljets$, we use only the `lowest' (loosest, highest rate) un-prescaled
triggers selecting two charged leptons~\cite{atlas_twiki_lowest_unprescaled}.
Those charged leptons are selected in the
high-level trigger (described in Section~\ref{sec:atlas_trigger})
primarily requiring large $\pt$ and certain quality criteria which vary by
trigger.

@@

\subsubsection{Alternative triggers}
Why should we only use two-lepton triggers?
Alternatives could be one-lepton triggers, for cases where the other is not
reconstructed at trigger level, or perhaps also triggers for jets and $\met$.
The answer is that the benefits of additional triggers were assessed to not
outweigh the cost of using using them.

The benefit of an additional trigger could be increased signal yields, if that
trigger do not also harmfully increase inseparable backgrounds.
A study, \textit{which was performed by Knut Vadla}, compared the efficiencies
of including one-lepton triggers.
In a signal-region-like selection requiring two leptons, two jets and
$\met > 200~\eV[G]$, this study showed that two-lepton triggers already accept
in excess of $90\%$ of events from benchmark C1N2 models.
Therefore any additional trigger can therefore have at most a $\approx10\%$;
improvement, and adding one-lepton triggers was found to increase efficiency by
only a few percentage points, depending on the model.
We considered that to be too little.

Costs of triggers are attributable to human effort; adding triggers requires
software work to include them and their associated Monte Carlo weights, along
with additional studies to validation of background estimates and evaluation of
systematic uncertainties.
Similarly, our implementation of the Matrix Method fake/non-prompt lepton
background estimate (see Section~\ref{sec:2ljets_mm_fakes}) is not equipped to
handle one-lepton triggers.

Although jet and $\met$ triggers were not studied in detail, they require
hard objects, such as $\ptjone \gtrsim 400~\eV[G]$ or
$\met \gtrsim 100~\eV[G]$~\cite{atlas_twiki_lowest_unprescaled}.
Leptons are striking signals which \atlas\ can trigger on with much softer
requirements; lepton triggers allow us to use softer jets and $\met$,
which are relied upon throughout the $\twoljets$ analyses.

@@

\subsection{Fake/non-prompt leptons}
\label{sec:2ljets_mm_fakes}
